---
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: sentence
---

# Study 1: OpenAlex Mean Citedness as a Proxy for Traditional Journal Metrics

We first tested whether OpenAlex's mean citedness can serve as a reliable proxy for more established journal-level impact metrics since we wanted to rely on openly available and non-commercial data.
If OpenAlex mean citedness tracks traditional metrics closely, it can be used with confidence in place of these proprietary indicators.
This study was exploratory and not preregistered.

```{r setup omc, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Method

We compared OpenAlex mean citedness against two established journal-level metrics: the Scimago Journal Rank (SJR), an openly available indicator conceptually similar to the JIF, and the Scimago "Citations per Document (2 years)" measure, which mirrors the JIF's two-year citation window.
Journal-level OpenAlex mean citedness values were merged with the 2024 Scimago dataset by journal title, retaining only journals for which both sources provided data.
Because the distributions of all three metrics are highly skewed, we assessed associations using Spearman rank correlations.
Figures were produced using `ggplot2` [@R-ggplot2] and arranged with `patchwork` [@R-patchwork].

```{r openalex-analysis, echo=FALSE, include=TRUE, fig.cap="Relationship between Open Alex Mean Citedness (OMC), Scimago Journal Rank (SJR) and Citation per Docs from Scimago."}
# Compare OpenAlex Mean Citedness with Scimago indicators
library(ggplot2)
library(patchwork)

# Journal Data (OpenAlex mean citedness)
mc <- read.csv("../Game/journaldata.csv")
names(mc) <- c("Title", "mc")
mc$mc <- as.numeric(sub(",", ".", mc$mc, fixed = TRUE))

# Scimago Journal Rank
jr <- read.csv("../Study/scimagojr 2024.csv", sep = ";")
jr$SJR <- as.numeric(sub(",", ".", jr$SJR, fixed = TRUE))
jr$mc2 <- as.numeric(sub(",", ".", jr$Citations...Doc...2years., fixed = TRUE))

# Merge datasets by journal name
mcjr <- merge(mc, jr, by = "Title")

# Number of journals
n_openalex <- nrow(mc)
n_matched  <- nrow(mcjr)

# Spearman correlations
ct_sjr <- suppressWarnings(cor.test(mcjr$SJR, mcjr$mc, method = "spearman"))
ct_mc2 <- suppressWarnings(cor.test(mcjr$mc2, mcjr$mc, method = "spearman"))

# APA 7 formatting helpers
fmt_p <- function(p) {
  if (p < .001) "< .001" else paste0("= ", sub("0\\.", ".", sprintf("%.3f", p)))
}
fmt_r <- function(r) sub("0\\.", ".", sprintf("%.2f", r))

rho_sjr <- as.numeric(ct_sjr$estimate)
p_sjr   <- ct_sjr$p.value
rho_mc2 <- as.numeric(ct_mc2$estimate)
p_mc2   <- ct_mc2$p.value

# Inline text strings (APA 7 / JARS)
apa_sjr <- paste0("*r*~s~ = ", fmt_r(rho_sjr),
                  ", *p* ", fmt_p(p_sjr),
                  ", *N* = ", n_matched)
apa_mc2 <- paste0("*r*~s~ = ", fmt_r(rho_mc2),
                  ", *p* ", fmt_p(p_mc2),
                  ", *N* = ", n_matched)

# Plot subtitles (plotmath)
sub_sjr <- bquote(italic(r)[s] == .(fmt_r(rho_sjr)) *
                  "," ~ italic(p) ~ .(fmt_p(p_sjr)) *
                  "," ~ italic(N) == .(n_matched))
sub_mc2 <- bquote(italic(r)[s] == .(fmt_r(rho_mc2)) *
                  "," ~ italic(p) ~ .(fmt_p(p_mc2)) *
                  "," ~ italic(N) == .(n_matched))

p1 <- ggplot(mcjr, aes(x = SJR, y = mc)) +
  geom_point() +
  xlab("Scimago Journal Rank") +
  ylab("OpenAlex Mean Citedness") +
  labs(subtitle = sub_sjr) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed")

p2 <- ggplot(mcjr, aes(x = mc2, y = mc)) +
  geom_point() +
  xlab("Citations per Docs (2 years)") +
  ylab("OpenAlex Mean Citedness") +
  labs(subtitle = sub_mc2) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed")

p1 + p2
```

## Results

Of the `r n_openalex` journals in the OpenAlex sample, `r n_matched` could be matched to entries in the Scimago database and were retained for the analyses.
OpenAlex mean citedness was strongly and positively correlated with the Scimago Journal Rank (`r apa_sjr`) as well as with Scimago's two-year citations-per-document metric (`r apa_mc2`).
As shown in the figure below, the relationships are close to monotonic, with most journals clustering near the identity line for the two-year citation measure, indicating that OpenAlex mean citedness produces values on a comparable scale to the JIF-like metric.

## Discussion

To summarize, OpenAlex mean citedness aligns closely with established journal-level impact indicators, showing strong rank-order agreement with both the Scimago Journal Rank and Scimago's two-year citations-per-document measure.
This supports the use of OpenAlex mean citedness as an open, freely accessible proxy for traditional metrics such as the JIF.
Given this correspondence, we rely on OpenAlex mean citedness in the following study, where openness and reproducibility of the data source are essential.
