```{r methods}

# This file only contains the methods

```

```{r methods-r-bib}

# Create a bib-file for R citations
# grateful::cite_packages(output = "file", bib.file = "r-references.bib")
papaja::r_refs(file = "r-references.bib")
r_citations <- papaja::cite_r(file = "r-references.bib")

```

```{r methods-jifopenalex}

# Compare OpenAlex Mean Citedness with JIF


# Journal Data (OpenAlex mean citedness)
# mc <- read.csv("../Game/journaldata.csv")

# Scimago Journal Rank (free and similar to JIF whereas Clarivates Journal Citation Report is paywalled)
# jr <- read.csv("../Study/scimagojr 2024.csv")

# Merge datasets by journal name
# mcjr <- merge(mc, jr, by = "issn")

# number of journals for which both values are available
# nrow(mc)
# nrow(mcjr)

# Relationship
# cor.test(mcjr$sjr, mcjr$mc)

# Plot
# ggplot(mcjr, aes(x = sjr, y = mc)) + geom_point() + xlab("Scimago Journal Rank") + ylab("OpenAlex Mean Citedness") + theme_bw()

```

# Methods

We collected predictions of replication success using an existing
community resource that includes pairs of replications and original
studies. Participants did not actually predict success since all of the
replication outcomes were publicly known. The primary purpose was not to
investigate how well researchers could predict replication outcomes but
if they relied on journal impact factors for this.

## Predicting Replicability

Past studies have used prediction markets with monetary rewards and
often before the replication success was known. Table X provides an
overview of past studies.

| Reference | Number of Studies | Field | Number of Transactions | Accuracy and Metric |
|---------------|---------------|---------------|---------------|---------------|
| @Dreber2015 | 44 | Psychology (RPP) | 2,496 | 39% actual success rate versus 55% predicted success rate |
| @Camerer2016 | 18 | Economics (EERP) | NA | 61.1% actual success rate versus 75.2% predicted success |
| @Camerer2018 | 21 | Social sciences | NA | 62% actual success rate versus 63.4% predicted success |
| @Gordon2021 | 103 | Social and behavioural sciences | NA | 73% accuracy |
| @Forsell2019 | 28 | Many Labs 2 | NA | 75% correct predictions |
| @Altmejd2019 | 144 | Combination of RPP, EERP, ML1 | None (AI models were used) | 70% accuracy (AUC =0.77) |

## Guess the Replication (GutheR): A Gamified Pedagogical Approach

To collect data on people's predictions of replicability and to drive
attention towards replication studies, we created a browser game that
resembles the popular guessthecorrelation.com. That is, the style is
pixelated, there are sounds for correct and wrong answers, players'
score will be ranked on a leaderboard, players get a certificate that
they can share with others on social media, and it can be played with
keyboard, mouse, or on smartphones.

The aim of Guess the Replication (GutheR) is to correctly predict
replication success based on only the title, abstract, study number (if
applicable) and - for 50% of the trials - the impact factor of the
original publication's journal. We used the FORRT Library of
Reproduction and Replication Attempts as the database from which trials
were created.

### Database: FLoRA

The FLoRA version from March 24, 2026 [@wallrich2026flora] was used to
create trials and enriched with data from OpenAlex
[@priem2022openalexfullyopenindexscholarly] and Crossref
[@Hendricks2020]. This database consist of over 1,500 pairs of
reproduction or replication studies including their coded result (e.g.,
success, failure, mixed) and an outcome quote. Thus, participants did
not actually predict the outcome. We filtered out all reproductions and
replications for which there was no informative outcome, such as studies
that were included in multi-replication articles and only said "success
rating = 1", "no", or other uninformative phrases. Furthermore, we
excluded specific large-scale multi-lab projects (e.g., Open Science
Collaboration, 2015). Finally, to allow the game to be less complex, we
excluded all studies for which the outcome rating was not "successful"
or "failed" and dropped any studies for which a sufficiently long
abstract could not be automatically retrieved via the Crossref or
OpenAlex APIs. The final sample consisted of [XXX] replication studies.
The dataset creation script is available online: [LINK]. We computed the
relationship between the journals' impact factors (defined as the 2-year
mean citedness via OpenAlex) and replication rate based on this subset
of the database.

### Procedure

Players of Guther had the option to read a tutorial describing the
procedure and options to use mouse or keyboard or start right away. An
"About" button on the starting screen provided information about
replications, FLoRA, data sharing, and credits/citation. When they
played the game for the first time, they had to choose a nickname that
would be presented on the leaderboard and create an anonymous personal
code made out of the first two letters of their city of birth, the last
wto letters of their father's first name, the last two digits of their
birth year, and the day of the month they were born. This would allow us
to link players if they played on different devices at different times
without having to collect sensitive data such as IP addresses.

Subsequently, we asked players three questions: What is your current
professional status (e.g., working outside of academia or being a PhD
student), what is your highest level of education (e.g., no formal
education, PhD), and how familiar are you with social research (e.g.,
unfamiliar, publishing social science research). Familiarity was
assessed using a multiple-choice format where participants could select
all statements that applied to them. Demographic inputs were cached
locally in the browser to prevent players from having to re-enter them
during subsequent sessions.

During the game, players saw their nickname, current score (+1 for every
correct response), their level (from "Junior Reviewer" to
"Editor-in-Chief" with level increases for every five correct
responses), and lives (3 at the beginning, losing one for every false
prediction). For each trial, we presented the original study's title
(e.g., "Turning the hands of time") and the corresponding abstract. For
half of the trials, we presented the journal's impact factor as computed
based on OpenAlex. Players had to predict "replicates" or "fails" by a
mouse click or button press. After their prediction, their guess, the
actual replication outcome, and whether they were correct or wrong,
accompanied by a high- versus low-pitched sound was presented. They had
the option to disable the sound. Moreover, we provided the quote from
the replication authors' about the success (e.g., "the data were 10.76
times more likely under the null hypothesis than under the alternative
hypothesis") and provided links to the original and replication study
[for this example @Topolinski2011 and @Wagenmakers2015]. Players
initiated the subsequent trial by pressing space or clicking the
respective button. Trials were drawn without replacement per user and
manipulated so that they had a forced 50% chance of being a study that
had successfully replicated versus failed.

Apart from the data that participants actively provided, we recorded
time spend on each of the trials so that we could filter out cases of
trials where players randomly pressed a button as well as whether they
switched browser tabs during a trial: Since the FLoRA is publicly
available and some replication attempts have already gained much
attention, players could otherwise look up the results. They could also
already know the results.

When losing all lives, a descending series of tones was played and
players could proceed to viewing the final results. At the top of the
page was an auto-generated Guther certificate of achievement, presenting
them a badge for the level that they achieved similar to the Open
Science Badges (for an example see
[https://www.cos.io/initiatives/badges](#0)) including how many
replication outcomes they predicted correctly. They could download the
certificate as a .png-file or share a text on Bluesky or Mastodon.
Below, we advertised replication-related projects from the FORRT
Replication Hub [e.g., @handbook] and presented the leaderboard as a
table with rank, player, score, and level. Table X contains the
leaderboard as of [DATE]. Players could then play again without having
to type in nickname, code, and respond to the career stage questions,
access the about page, or report issues on Github. The number of rounds
that players could play was unlimited.

## Analysis Plan

*Note: This section is written in past tense for consistency with the
final manuscript. The analysis plan, including the complete R code, was
preregistered prior to data collection and analysis [OSF LINK].*

All analyses were conducted in `r r_citations`. We followed the LEVEL
reporting guidelines for multilevel analyses [@Monsalves2020].

### Data Exclusion Criteria

We applied exclusion criteria at two levels. At the session level, we
flagged and removed sessions with fewer than five completed trials,
sessions exhibiting bot-like behavior (coefficient of variation of
reaction times below 0.10), and sessions showing straightlining (10 or
more identical consecutive responses with a median reaction time below
2,000 ms). At the trial level, we excluded individual trials in which
the participant switched browser tabs (indicating possible look-up of
the replication outcome), trials with reaction times below 2,000 ms
(insufficient time to read the abstract), and trials with reaction times
exceeding 900,000 ms (15 minutes, indicating abandonment).

### Multilevel Data Structure

The data had a hierarchical structure: individual trials (Level 1) were
nested within participants (Level 2), identified by their anonymous
personal code. Because multiple participants could judge the same
replication–original study pair, and each participant judged multiple
studies, study identity and participant identity were crossed rather than
nested. We included a crossed random effect for study identity only if
the final analytic sample exceeded 5,000 observations; otherwise, we
retained a two-level model with participants as the sole grouping
factor. Table \@ref(tab:multilevel-diagram) presents the multilevel
diagram.

```{r multilevel-diagram, echo=FALSE, results='asis'}
mlm_diagram <- data.frame(
  Level = c("Person (Level 2)", "Trial (Level 1)"),
  Index = c("$$j = 1, \\ldots, J$$", "$$i = 1, \\ldots, n_j$$"),
  Variables = c(
    "Between-subject: in\\_research (research experience: yes/no)",
    paste0(
      "Within-subject: if\\_visible (impact factor shown: yes/no), ",
      "impact\\_factor (journal mean citedness), ",
      "true\\_outcome (replication success/failure), ",
      "reaction\\_time (ms), abstract\\_length (characters)"
    )
  ),
  Outcome = c(
    "---",
    "player\\_guess (success = 1, failure = 0)"
  ),
  `Random Effects` = c(
    "Random intercept (and possibly random slopes; see fallback chain)",
    "---"
  ),
  check.names = FALSE
)

knitr::kable(
  mlm_diagram,
  caption = "Multilevel diagram for the analysis of replication predictions.",
  booktabs = TRUE,
  escape = FALSE,
  format = "pandoc"
)
```

The dependent variable---the participant's binary prediction of
replication success---was measured at Level 1. Because the outcome was
at a lower level than the grouping variable, a multilevel analysis was
required. The within-subject manipulation of impact factor visibility
and the between-subject variation in research experience motivated the
inclusion of both fixed and random effects to account for the correlated
structure of trials within participants.

### Variable Definitions

*Dependent variable.* `player_guess` was coded 1 if the participant
predicted "success" (i.e., the original study replicates) and 0 if they
predicted "failure."

*Primary predictors.* `if_visible` was a within-subject binary indicator
of whether the journal's impact factor was displayed on a given trial.
`in_research` was a between-subject binary indicator coded 1 if the
participant reported being a PhD student, postdoc, or professor, or
held a PhD, and 0 otherwise. `impact_factor` was the 2-year mean
citedness of the original study's journal as obtained from OpenAlex;
this value was present in the data for every trial regardless of whether
it was shown to the participant, allowing us to model its influence on
guessing behavior as a function of its visibility.

*Control variables.* `true_outcome` indicated whether the original study
actually replicated successfully. `reaction_time` was the time in
milliseconds from trial onset to the participant's response.
`abstract_length` was the character count of the original study's
abstract.

*Grouping variables.* `personal_code` identified participants.
`study_id` identified unique replication–original study pairings.

### Feature Engineering and Preregistered Transformation Rule

For each continuous predictor (`impact_factor`, `reaction_time`,
`abstract_length`), we computed the skewness. If the absolute skewness
exceeded 1, we applied a $\log(1+x)$ transformation prior to
$z$-standardization; otherwise, we only $z$-standardized. This
data-driven transformation rule was preregistered to ensure that the
decision was transparent and reproducible.

We additionally assessed the linearity of each continuous predictor on
the logit scale by fitting a generalized additive model (GAM) with
penalized splines using the `mgcv` package [@R-mgcv]. If the smooth
term for `abstract_length` was statistically significant at
$\alpha = .05$ (indicating meaningful nonlinearity), we included a
quadratic term ($\text{abstract\_length}_z^2$) in the final model.

### Descriptive Analyses

Following the LEVEL recommendations, we reported descriptive statistics
at each level of the data hierarchy.

At Level 1 (trial level), we reported the proportion of "success"
predictions, the proportion of trials in which the impact factor was
visible, the proportion of trials with a successful true outcome, and
means and standard deviations for reaction time, impact factor, and
abstract length. Standard errors and 95% confidence intervals for these
statistics were adjusted for the clustering of trials within
participants using a survey design framework [the `survey` package;
@R-survey].

At Level 2 (participant level), we reported the number of participants,
the distribution of trials per participant (median and range), and the
distribution of research experience. We presented participant-level
means of the dependent variable, broken down by research experience and
impact factor visibility (spaghetti plots showing within-subject changes
across conditions). Bivariate plots of continuous predictors against the
dependent variable identified cluster membership by color or faceting.

We also presented correlation matrices separately for Level 1
(trial-level variables) and Level 2 (participant-aggregated variables).

### Model Specification

We estimated three generalized linear mixed models (GLMMs) with a
binomial distribution and logit link function, using maximum likelihood
estimation via the Laplace approximation as implemented in
`lme4::glmer` [@R-lme4]. All models used the `bobyqa` optimizer with a
maximum of 100,000 function evaluations.

*Null model.* The null model contained no predictors and included only a
random intercept for participants:

$$
\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + u_{0j}
$$

where $Y_{ij}$ was the binary prediction of participant $j$ on trial
$i$, $\beta_0$ was the fixed intercept, and
$u_{0j} \sim N(0, \sigma^2_{u0})$ was the random intercept for
participant $j$. This model served to estimate the baseline variance
partition coefficient (VPC), quantifying how much of the total variance
in predictions was attributable to between-participant differences.

*Intermediate model.* The intermediate model added the between-subject
predictor (research experience), the within-subject experimental
manipulation (impact factor visibility), their interaction, and the true
replication outcome as a control, with a random intercept for
participants:

$$
\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + \beta_1 \cdot
\text{in\_research}_j + \beta_2 \cdot \text{if\_visible}_{ij} + \beta_3
\cdot \text{in\_research}_j \times \text{if\_visible}_{ij} + \beta_4
\cdot \text{true\_outcome}_{ij} + u_{0j}
$$

This model tested whether the experimental manipulation and research
experience affected predictions before introducing continuous
covariates.

*Final model.* The final model extended the intermediate model with the
three-way interaction between research experience, impact factor
visibility, and the (standardized) impact factor value, plus continuous
control variables:

$$
\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + (\beta_1 \cdot
\text{in\_research}_j \times \text{if\_visible}_{ij} \times
\text{impact\_factor\_z}_{ij}) + \beta_2 \cdot
\text{true\_outcome}_{ij} + \beta_3 \cdot
\text{reaction\_time\_z}_{ij} + \beta_4 \cdot
\text{abstract\_length\_z}_{ij} + \mathbf{u}_j
$$

where $\mathbf{u}_j$ denoted the vector of participant-level random
effects. The three-way interaction
$\text{in\_research} \times \text{if\_visible} \times \text{impact\_factor\_z}$
was the term of primary theoretical interest: it tested whether the
effect of the impact factor on participants' predictions depended on
(a) whether the impact factor was actually shown and (b) whether the
participant had research experience. If the three-way interaction model
failed to converge under any random-effects structure (see below), we
fell back to a two-way interaction model
($\text{in\_research} \times \text{if\_visible} + \text{impact\_factor\_z}$)
and reported both attempts.

### Random-Effects Structure and Preregistered Fallback Chain

Specifying the random-effects structure of GLMMs involved a trade-off
between theoretical fidelity and empirical estimability. We preregistered
a sequential fallback chain, attempting the most complex theoretically
justified structure first and simplifying only upon convergence failure
or singular fit (defined as any variance component estimated at or near
zero, assessed via `isSingular()` with a tolerance of $10^{-4}$). The
chain proceeded as follows:

1.  **Correlated random slopes:**
    $(1 + \text{if\_visible} + \text{if\_visible} \times \text{impact\_factor\_z} + \text{true\_outcome} \mid \text{personal\_code})$
2.  **Uncorrelated random slopes:** same terms with $\|$ instead of
    $\mid$ (diagonal covariance matrix)
3.  **Drop true\_outcome from random part:**
    $(1 + \text{if\_visible} + \text{if\_visible} \times \text{impact\_factor\_z} \| \text{personal\_code})$
4.  **Replace interaction with main effect:**
    $(1 + \text{if\_visible} + \text{impact\_factor\_z} \| \text{personal\_code})$
5.  **Random slope for visibility only:**
    $(1 + \text{if\_visible} \| \text{personal\_code})$
6.  **Random intercept only:**
    $(1 \mid \text{personal\_code})$
7.  **No random effects (fallback):** ordinary logistic regression via
    `glm()`

We reported which step of the chain was used and the corresponding model
formula. If the final model included correlated random effects (Step 1),
we reported the estimated correlation structure among the random
effects. If the analytic sample exceeded 5,000 observations, we
additionally included a crossed random intercept for study identity at
each step: $(1 \mid \text{study\_id})$.

### Assumption and Diagnostic Checks

We conducted the following checks on the final model:

1.  *Convergence and singularity:* We verified that the optimizer
    converged without warnings and that the model was not singular.
2.  *Complete or quasi-complete separation:* We tested for perfect
    separation in the fixed-effects design matrix using the
    `detectseparation` package [@R-detectseparation]. If separation was
    detected, coefficient estimates and standard errors were considered
    unreliable, and we would have considered penalized estimation (e.g.,
    Firth's correction).
3.  *Multicollinearity:* We computed generalized variance inflation
    factors (GVIFs) for all non-interaction fixed effects using
    `car::vif` [@R-car]. Values exceeding 10 were flagged.
4.  *Random-effects normality:* We inspected QQ plots of the estimated
    random effects (BLUPs) for each random-effects term.
5.  *Linearity on the logit scale:* We compared the GLMM with a GAM
    that replaced linear terms with penalized splines. Effective degrees
    of freedom near 1 indicated linearity; values substantially above 1
    indicated potential nonlinearity.
6.  *Residual diagnostics:* We used simulation-based residual
    diagnostics via the `DHARMa` package [@R-DHARMa], including tests
    for overdispersion and outliers.

### Model Comparison and Fit Indices

We compared the null, intermediate, and final models using the following
criteria:

-   *Variance partition coefficient (VPC):* The proportion of total
    variance attributable to between-participant differences, computed
    from the variance components of each model. We reported VPCs for
    each model to show how the inclusion of predictors explained
    between-participant variation.
-   *Akaike Information Criterion (AIC)* and *Bayesian Information
    Criterion (BIC):* Lower values indicated better model fit with
    parsimony penalties.
-   *Area Under the Receiver Operating Characteristic Curve (AUC):*
    Computed from in-sample predicted probabilities using the `pROC`
    package [@R-pROC]. The AUC quantified the model's discriminative
    ability, that is, how well predicted probabilities distinguished
    between "success" and "failure" predictions.

Fixed effects were reported as odds ratios (ORs) with Wald-based 95%
confidence intervals and $p$-values. A summary table presented these
estimates alongside VPCs, AIC, BIC, and AUC for all three models,
following the tabular format recommended by the LEVEL guidelines
[@Monsalves2020].

### Sample Size Considerations

Because participant recruitment occurred through voluntary engagement
with an online game, the sample size was not predetermined by a formal
power analysis. Instead, we reported the final number of participants
and trials at each level after applying all exclusion criteria. We
reported the median and range of trials per participant, as the number
of trials varied across participants depending on their game performance
(i.e., how many lives they retained). The VPCs estimated from the null
model were used to compute post-hoc variance inflation factors
($\text{VIF} = 1 + (\bar{n}_j - 1) \times \text{VPC}$, where
$\bar{n}_j$ was the average number of trials per participant) to
contextualize the effective sample size.