```{r methods}

# This file only contains the methods

```

```{r methods-r-bib}

# Create a bib-file for R citations
# grateful::cite_packages(output = "file", bib.file = "r-references.bib")
papaja::r_refs(file = "r-references.bib")
r_citations <- papaja::cite_r(file = "r-references.bib")

```

```{r methods-descriptive-information}

# Calculate the age and sd of the participants

# mean_age <- mean(dataSCR$age_T0, na.rm = TRUE)
# sd_age <- sd(dataSCR$age_T0, na.rm = TRUE)

```

# Methods

## Predicting Replicability

-   prediction markets [create beautiful table with source, number of studies, field, number of participants, accuracy (and accuracy metric)
    -   <https://doi.org/10.1073/pnas.1516179112> prediction of outcomes from OSC (2015)
    -   <https://doi.org/10.1126/science.aaf0918> prediction market in Camerer 2016
    -   <https://doi.org/10.1038/s41562-018-0399-z> prediction market for Camerer 2018 ???
    -   <https://doi.org/10.1371/journal.pone.0248780> prediction market on pooled data, 73% accuracy, XXX studies, XXX participants
    -   <https://doi.org/10.1016/j.joep.2018.10.009> Predicting Many Labs 2
    -   <https://doi.org/10.1371/journal.pone.0225826> AI models that predict replication outcomes, 71% accuracy (AUC?)
    -   SMART competition

## Guess the Replication (Guther): A Gamified Pedagogical Approach

## Analysis Plan

For data analysis and visualizations as well as for the creation of the manuscript, we used `r r_citations`.
