------------------------------------------------------------------------

```{r methods, include=FALSE}

# This file only contains the methods

```

```{r methods-r-bib, include=FALSE}

# Create a bib-file for R citations
# grateful::cite_packages(output = "file", bib.file = "r-references.bib")
# papaja::r_refs(file = "r-references.bib", append = FALSE)


r_citations <- papaja::cite_r(file = "r-references.bib")
```

# Study 3: Guess the Replication (GutheR) - A Gamified Pedagogical Approach

We collected predictions of replication success using an existing
community resource that includes pairs of replications and original
studies. Participants did not actually predict success since all of the
replication outcomes were publicly known. The primary purpose was not to
investigate how well researchers could predict replication outcomes but
if they relied on journal's citation numbers for this.

## Predicting Replicability

Past studies have used prediction markets with monetary rewards and
often before the replication success was known. Table
\@ref(tab:prediction-studies) provides an overview of past studies.

```{r prediction-studies, echo=FALSE, include=TRUE}

library(knitr)

prediction_data <- data.frame(
  Reference = c("@Dreber2015", "@Camerer2016", "@Camerer2018",
                 "@Gordon2021", "@Forsell2019", "@Altmejd2019"),
  `Number of Studies` = c(44, 18, 21, 103, 28, 144),
  Field = c("Psychology (RPP)", "Economics (EERP)", "Social sciences",
            "Social and behavioural sciences", "Many Labs 2",
            "Combination of RPP, EERP, ML1"),
  `Number of Transactions` = c("2,496", "NA", "NA", "NA", "NA",
                                "None (AI models were used)"),
  `Accuracy and Metric` = c(
    "39% actual success rate versus 55% predicted success rate",
    "61.1% actual success rate versus 75.2% predicted success",
    "62% actual success rate versus 63.4% predicted success",
    "73% accuracy",
    "75% correct predictions",
    "70% accuracy (AUC = 0.77)"
  ),
  check.names = FALSE
)

kable(prediction_data, format = "latex", booktabs = TRUE,
      caption = "Overview of past studies predicting replication outcomes.",
      col.names = c("Reference", "Number of Studies", "Field",
                     "Number of Transactions", "Accuracy and Metric"))



# # Markdown table backup
# | Reference | Number of Studies | Field | Number of Transactions | Accuracy and Metric |
# |---------------|---------------|---------------|---------------|---------------|
# | @Dreber2015 | 44 | Psychology (RPP) | 2,496 | 39% actual success rate versus 55% predicted success rate |
# | @Camerer2016 | 18 | Economics (EERP) | NA | 61.1% actual success rate versus 75.2% predicted success |
# | @Camerer2018 | 21 | Social sciences | NA | 62% actual success rate versus 63.4% predicted success |
# | @Gordon2021 | 103 | Social and behavioural sciences | NA | 73% accuracy |
# | @Forsell2019 | 28 | Many Labs 2 | NA | 75% correct predictions |
# | @Altmejd2019 | 144 | Combination of RPP, EERP, ML1 | None (AI models were used) | 70% accuracy (AUC =0.77) |
```

(#tab:prediction-studies) Predictions of replication outcomes in past
studies.

| Reference | Number of Studies | Field | Accuracy and Metric |
|------------------|------------------|------------------|------------------|
| @Dreber2015 | 44 | Psychology (RPP) | 39% actual success rate versus 55% predicted success rate |
| @Camerer2016 | 18 | Economics (EERP) | 61.1% actual success rate versus 75.2% predicted success |
| @Camerer2018 | 21 | Social sciences | 62% actual success rate versus 63.4% predicted success |
| @Gordon2021 | 103 | Social and behavioural sciences | 73% accuracy |
| @Forsell2019 | 28 | Many Labs 2 | 75% correct predictions |
| @Altmejd2019 | 144 | Combination of RPP, EERP, ML1 | 70% accuracy (AUC =0.77) |

## Method

To collect data on people's predictions of replicability and to drive
attention towards replication studies, we created a browser game that
resembles the popular guessthecorrelation.com [@Wagih2015]. That is, the
style is pixelated, there are sounds for correct and wrong answers,
players' scores will be ranked on a leaderboard, players get a
certificate that they can share with others on social media, and it can
be played with keyboard, mouse, or on smartphones.

The aim of Guess the Replication (GutheR) is to correctly predict
replication success based on only the title, abstract, study number (if
applicable) and - for approximately 50% of the trials - the OMC of the
original publication's journal. We used the *FORRT Library of
Reproduction and Replication Attempts* (FLoRA) as the database from
which trials were created.

All analyses were conducted in R version `r getRversion()` [@R-base].
The manuscript was prepared with `rmarkdown` [@R-rmarkdown], `knitr`
[@R-knitr], and `papaja` [@R-papaja]; package citations were managed
with `grateful` [@R-grateful]. Data wrangling relied on the `tidyverse`
[@R-tidyverse], including `dplyr` [@R-dplyr], `tidyr` [@R-tidyr],
`readr` [@R-readr], `purrr` [@R-purrr], `stringr` [@R-stringr], `tibble`
[@R-tibble], `forcats` [@R-forcats], and `lubridate` [@R-lubridate].
Descriptive statistics were computed with `psych` [@R-psych],
inferential tests with `car` [@R-car], effect sizes with `effectsize`
[@R-effectsize], and *z*-curve analyses with `zcurve` [@R-zcurve].
Numeric values were formatted with `prmisc` [@R-prmisc]. Figures were
produced with `ggplot2` [@R-ggplot2] and combined using `patchwork`
[@R-patchwork], `cowplot` [@R-cowplot], with axis scales formatted via
`scales` [@R-scales]. Tables and spreadsheets were prepared with
`flextable` [@R-flextable], `kableExtra` [@R-kableExtra], and `openxlsx`
[@R-openxlsx]. Additional modeling described in the OpenAlex mean
citedness section used `mgcv` [@R-mgcv], `lme4` [@R-lme4], `rms`
[@R-rms], `pROC` [@R-pROC], `DHARMa` [@R-DHARMa], and `detectseparation`
[@R-detectseparation]. To ensure computational reproducibility, project
dependencies were managed with `renv` [@R-renv].

### Database: FLoRA

The FLoRA version from April 24, 2026 [@wallrich2026flora] was used to
create trials and enriched with data from OpenAlex
[@priem2022openalexfullyopenindexscholarly] and Crossref
[@Hendricks2020]. This database now consists of over 2,000 pairs of
reproduction or replication studies including their coded result (e.g.,
success, failure, mixed) and an outcome quote. The database is updated
daily and available at <https://github.com/forrtproject/FReD-data>.
Thus, participants did not actually predict the outcome. We filtered out
all reproductions (e.g., repeated tests that used the same data as the
original study). Finally, to allow the game to be less complex, we
excluded all studies for which the outcome rating was not "successful"
or "failed" and dropped any studies for which a sufficiently long
abstract could not be automatically retrieved via the Crossref or
OpenAlex APIs. The final sample consisted of 1,234 pairs of original and
replication studies (565 failures, 670 successes). The dataset creation
script is available online:
<https://github.com/LukasRoeseler/GuessTheReplication/blob/main/Game/dataset.csv>
(long-term archival via the Open Science Framework is planned alongside
the preregistration). We computed the relationship between the journals'
impact factors (defined as the 2-year mean citedness via OpenAlex) and
replication rate based on this subset of the database.

### Informed Consent

Before accessing the game, participants were presented with a consent
modal. They were informed that participation was voluntary, that they
must be at least 18 years old, that data would be stored via Supabase
and published on Zenodo or OSF under a CC-BY license for at least ten
years, and that they could request deletion of their data by contacting
the research team with their personal code. Participants had to check a
box confirming they had read and understood the privacy policy before
they could proceed. Consent status was stored locally in the browser so
that returning players were not asked again.

### Procedure

Players of GutheR had the option to read a tutorial describing the
procedure and options to use mouse or keyboard or start right away. An
"About" button on the starting screen provided information about
replications, FLoRA, data sharing, and credits/citation. When they
played the game for the first time, they had to choose a nickname that
would be presented on the leaderboard and create an anonymous personal
code made out of the first two letters of their city of birth, the last
two letters of their father's first name, the last two digits of their
birth year, and the day of the month they were born. This would allow us
to link players if they played on different devices at different times
without having to collect sensitive data such as IP addresses.

Subsequently, we asked players three questions: (1) What is your current
professional status? (response options: student at university, PhD
student, postdoc, professor, working outside of research, unemployed,
other), (2) What is your highest level of education? (response options:
no formal qualification, high school diploma, apprenticeship, bachelor's
degree, master's degree, PhD), and (3) If you do research, what
discipline are you most familiar with? (optional free-text field, e.g.,
Psychology, Economics). Demographic inputs were cached locally in the
browser to prevent players from having to re-enter them during
subsequent sessions.

During the game, players saw their nickname, current score (+1 for every
correct response), their level (from "Junior Reviewer" to
"Editor-in-Chief" with level increases for every five correct
responses), and lives (5 at the beginning, losing one for every false
prediction, and gaining one bonus life for every level-up, i.e., every
five correct responses). For each trial, we presented the original
study's title (e.g., "Turning the hands of time") and the corresponding
abstract. For half of the trials, we presented the two-year OpenAlex
Mean Citedness (OMC). Players had to predict "replicates" or "fails" by
a mouse click or button press. After their prediction, their guess, the
actual replication outcome, and whether they were correct or wrong,
accompanied by a high- versus low-pitched sound was presented. They had
the option to disable the sound. Moreover, we provided the quote from
the replication authors' about the success (e.g., "the data were 10.76
times more likely under the null hypothesis than under the alternative
hypothesis") where applicable and provided links to the original and
replication study [for this example @Topolinski2011 and
@Wagenmakers2015]. Players initiated the subsequent trial by pressing
space or clicking the respective button. Trials were drawn without
replacement per user and manipulated so that they had a forced 50%
chance of being a study that had successfully replicated versus failed.

Apart from the data that participants actively provided, we recorded
time spent on each of the trials so that we could filter out cases of
trials where players randomly pressed a button as well as whether they
switched browser tabs during a trial: Since the FLoRA is publicly
available and some replication attempts have already gained much
attention, players could otherwise look up the results. They could also
already know the results.

When a player's score crossed a level threshold (every five correct
predictions), a level-up screen was displayed showing their new rank
badge, rank name, and a notification that one bonus life had been
awarded, accompanied by a distinct ascending jingle. Players then
continued to the next trial.

When losing all lives (or when all available studies had been
exhausted), a descending series of tones was played on the feedback
screen. Before viewing their final results, players were presented with
a data integrity check. They were asked to indicate whether they had
looked up any of the studies before making a prediction or had randomly
pressed buttons without paying attention. They were informed that their
response would not affect their leaderboard position or certificate but
that their data would be excluded from the research analysis if they
indicated that they had looked up responses or clicked randomly. This
self-report was stored as a boolean variable (`data_integrity_keep`)
alongside each session's score data.

At the top of the page was an auto-generated GutheR certificate of
achievement, presenting them a badge for the level that they achieved
similar to the Open Science Badges (for an example see
[https://www.cos.io/initiatives/badges](#0)) including how many
replication outcomes they predicted correctly. They could download the
certificate as a .png-file or share a text on Bluesky or Mastodon.
Below, we advertised replication-related projects from the FORRT
Replication Hub [e.g., @handbook] and presented the leaderboard as a
table with rank, player, score, and level. Table X contains the
leaderboard as of [DATE]. Players could then play again without having
to type in nickname, code, and respond to the career stage questions,
access the about page, or report issues on Github. The number of rounds
that players could play was unlimited.

## Analysis Plan

\*Note: This section is written in past tense for consistency with the
final manuscript. The analysis plan, including the complete R code, was
preregistered prior to data collection and analysis on the OSF
[@Roseler2026osf]. In the case of discrepancies between this narrative
analysis plan and the analysis script, the analysis script has higher
authority.\*

All analyses were conducted in `r r_citations`. We followed the LEVEL
reporting guidelines for multilevel analyses [@monsalves2020level].

### Data Exclusion Criteria

We applied exclusion criteria at two levels. At the session level, we
flagged and removed sessions with fewer than five completed trials,
sessions exhibiting bot-like behavior (coefficient of variation of
reaction times below 0.10), and sessions showing straightlining (10 or
more identical consecutive responses with a median reaction time below
3,000 ms). At the trial level, we excluded individual trials in which
the participant switched browser tabs (indicating possible look-up of
the replication outcome), trials with reaction times below 2,000 ms
(insufficient time to read the abstract), and trials with reaction times
exceeding 900,000 ms (15 minutes, indicating abandonment).

### Multilevel Data Structure

The data had a hierarchical structure: individual trials (Level 1) were
nested within participants (Level 2), identified by their anonymous
personal code. Because multiple participants could judge the same
replication–original study pair, and each participant judged multiple
studies, study identity and participant identity were crossed rather
than nested. We included a crossed random effect for study identity only
if the final analytic sample exceeded 5,000 observations; otherwise, we
retained a two-level model with participants as the sole grouping
factor. Table \@ref(tab:multilevel-diagram) presents the nesting
structure.

(#tab:multilevel-diagram) Table of the nesting structure.

```{r multilevel-diagram, echo=FALSE, include=TRUE}

mlm_diagram <- data.frame(
  Level = c("Person (Level 2)", "Trial (Level 1)"),
  Index = c("$$j = 1, \\ldots, J$$", "$$i = 1, \\ldots, n_j$$"),
  Variables = c(
    "Between-subject: in\\_research (research experience: yes/no)",
    paste0(
      "Within-subject: if\\_visible (OMC shown: yes/no), ",
      "impact\\_factor (journal mean citedness), ",
      "true\\_outcome (replication success/failure), ",
      "reaction\\_time (ms), abstract\\_length (characters)"
    )
  ),
  Outcome = c(
    "---",
    "player\\_guess (success = 1, failure = 0)"
  ),
  `Random Effects` = c(
    "Random intercept (and possibly random slopes; see fallback chain)",
    "---"
  ),
  check.names = FALSE
)

knitr::kable(
  mlm_diagram,
  caption = "Multilevel diagram for the analysis of replication predictions.",
  booktabs = TRUE,
  escape = FALSE,
  format = "pandoc"
)
```

The dependent variable, the participant's binary prediction of
replication success, was measured at Level 1. A multilevel analysis was
required because the outcome was at a lower level than the grouping
variable. The within-subject manipulation of OMC visibility and the
between-subject variation in research experience motivated the inclusion
of both fixed and random effects to account for the correlated structure
of trials within participants [@monsalves2020level].

### Variable Definitions

*Dependent variable.* `player_guess` was coded 1 if the participant
predicted "success" (i.e., the original study replicates) and 0 if they
predicted "failure."

*Primary predictors.* `if_visible` was a within-subject binary indicator
of whether the journal's OMC was displayed on a given trial.
`in_research` was a between-subject binary indicator coded 1 if the
participant reported being a PhD student, postdoc, or professor, or held
a PhD, and 0 otherwise. `impact_factor` was the 2-year mean citedness of
the original study's journal as obtained from OpenAlex; this value was
present in the data for every trial regardless of whether it was shown
to the participant, allowing us to model its influence on guessing
behavior as a function of its visibility.

*Control variables.* `true_outcome` indicated whether the original study
actually replicated successfully. `reaction_time` was the time in
milliseconds from trial onset to the participant's response.
`abstract_length` was the character count of the original study's
abstract.

*Grouping variables.* `personal_code` identified participants.
`study_id` identified unique replication–original study pairings.

### Feature Engineering and Preregistered Transformation Rule

For each continuous predictor (`impact_factor`, `reaction_time`,
`abstract_length`), we computed the skewness. If the absolute skewness
exceeded 1, we applied a $\log(1+x)$ transformation prior to
$z$-standardization; otherwise, we only $z$-standardized. This
data-driven transformation rule was preregistered to ensure that the
decision was transparent and reproducible.

We additionally assessed the linearity of each continuous predictor on
the logit scale by fitting a generalized additive model (GAM) with
penalized splines using the `mgcv` package [@R-mgcv]. If the smooth term
for `abstract_length` was statistically significant at $\alpha = .05$
and exhibited meaningful nonlinearity, operationalized as estimated
degrees of freedom \>2, we included a quadratic term
$(\text{abstract_length}_{z})^{2}$ in the final model.

### Descriptive Analyses

We conducted descriptive statistics at each level of the data hierarchy.

At Level 1 (trial level), we reported the proportion of "success"
predictions, the proportion of trials in which the OMC was visible, the
proportion of trials with a successful true outcome, and means and
standard deviations for reaction time, OMC, and abstract length.
Standard errors and 95% confidence intervals for these statistics were
adjusted for the clustering of trials within participants using a survey
design framework [the `survey` package; @R-survey].

At Level 2 (participant level), we reported the number of participants,
the distribution of trials per participant (median and range), and the
distribution of research experience. We presented participant-level
means of the dependent variable, broken down by research experience and
OMC visibility (spaghetti plots showing within-subject changes across
conditions). Bivariate plots of continuous predictors against the
dependent variable identified cluster membership by color or faceting.

We also presented correlation matrices separately for Level 1
(trial-level variables) and Level 2 (participant-aggregated variables).

### Model Specification

We estimated three generalized linear mixed models (GLMMs) with a
binomial distribution and logit link function, using maximum likelihood
estimation via the Laplace approximation as implemented in `lme4::glmer`
[@R-lme4]. All models used the `bobyqa` optimizer with a maximum of
100,000 function evaluations. Following the LEVEL recommendations, we
report null model and intermediate model, so that the impact of
explanatory variables on variance components can be easily identified.

*Null model.* The null model contained no predictors and included only a
random intercept for participants:

$$\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + u_{0j}$$

where $Y_{ij}$ was the binary prediction of participant $j$ on trial
$i$, $\beta_0$ was the fixed intercept, and
$u_{0j} \sim N(0, \sigma^2_{u0})$ was the random intercept for
participant $j$. This model served to estimate the baseline variance
partition coefficient (VPC), quantifying how much of the total variance
in predictions was attributable to between-participant differences.

*Intermediate model.* The intermediate model added the between-subject
predictor (research experience), the within-subject experimental
manipulation (OMC visibility), their interaction, and the true
replication outcome as a control, with a random intercept for
participants:

$$\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + \beta_1 \cdot
\text{in_research}_j + \beta_2 \cdot \text{if_visible}_{ij} + \beta_3
\cdot \text{in_research}_j \times \text{if_visible}_{ij} + \beta_4
\cdot \text{true_outcome}_{ij} + u_{0j}$$

This model tested whether experimental manipulation and research
experience affected predictions before introducing continuous
covariates.

*Final model.* The final model extended the intermediate model with the
three-way interaction between research experience, OMC visibility, and
the (standardized) OMC value, plus continuous control variables:

$$\text{logit}\bigl(P(Y_{ij} = 1)\bigr) = \beta_0 + (\beta_1 \cdot
\text{in_research}_j \times \text{if_visible}_{ij} \times
\text{impact_factor_z}_{ij}) + \beta_2 \cdot
\text{true_outcome}_{ij} + \beta_3 \cdot
\text{reaction_time_z}_{ij} + \beta_4 \cdot
\text{abstract_length_z}_{ij} + \mathbf{u}_j$$

where $\mathbf{u}_j$ denoted the vector of participant-level random
effects. The three-way interaction
$\text{in_research} \times \text{if_visible} \times \text{impact_factor_z}$
was the term of primary theoretical interest: it tested whether the
effect of the OMC on participants' predictions depended on (a) whether
the OMC was actually shown and (b) whether the participant had research
experience. If the three-way interaction model failed to converge under
any random-effects structure (see below), we fell back to a two-way
interaction model
($\text{in_research} \times \text{if_visible} + \text{impact_factor_z}$)
and reported both attempts.

### Random-Effects Structure and Preregistered Fallback Chain

Specifying the random-effects structure of GLMMs involved a trade-off
between theoretical fidelity and empirical estimation quality. We
preregistered a sequential fallback chain, attempting the most complex
theoretically justified structure first and simplifying only upon
convergence failure or singular fit (defined as any variance component
estimated at or near zero, assessed via `isSingular()` with a tolerance
of $10^{-4}$). The chain proceeded as follows:

1.  **Correlated random slopes:**
    $(1 + \text{if_visible} + \text{if_visible} \times \text{impact_factor_z} + \text{true_outcome} \mid \text{personal_code})$
2.  **Uncorrelated random slopes:** same terms with $\|$ instead of
    $\mid$ (diagonal covariance matrix)
3.  **Drop true_outcome from random part:**
    $(1 + \text{if_visible} + \text{if_visible} \times \text{impact_factor_z} \| \text{personal_code})$
4.  **Replace interaction with main effect:**
    $(1 + \text{if_visible} + \text{impact_factor_z} \| \text{personal_code})$
5.  **Random slope for visibility only:**
    $(1 + \text{if_visible} \| \text{personal_code})$
6.  **Random intercept only:** $(1 \mid \text{personal_code})$
7.  **No random effects (fallback):** ordinary logistic regression via
    `glm()`

We reported which step of the chain was used and the corresponding model
formula. If the final model included correlated random effects (Step 1),
we reported the estimated correlation structure among the random
effects. If the analytic sample exceeded 5,000 observations, we
additionally included a crossed random intercept for study identity at
each step: $(1 \mid \text{study_id})$.

### Assumption and Diagnostic Checks

We conducted the following checks on the final model:

1.  *Convergence and singularity:* We verified that the optimizer
    converged without warnings and that the model was not singular.
2.  *Complete or quasi-complete separation:* We tested for perfect
    separation in the fixed-effects design matrix using the
    `detectseparation` package [@R-detectseparation]. If separation was
    detected, coefficient estimates and standard errors were considered
    unreliable, and we would have considered penalized estimation (e.g.,
    Firth's correction).
3.  *Multicollinearity:* We computed generalized variance inflation
    factors (GVIFs) for all non-interaction fixed effects using
    `car::vif` [@R-car]. Values exceeding 10 were flagged.
4.  *Random-effects normality:* We inspected QQ plots of the estimated
    random effects (BLUPs) for each random-effects term.
5.  *Linearity on the logit scale:* We compared the GLMM with a GAM that
    replaced linear terms with penalized splines. Effective degrees of
    freedom near 1 indicated linearity; significant values substantially
    above 2 indicated potential nonlinearity.
6.  *Residual diagnostics:* We used simulation-based residual
    diagnostics via the `DHARMa` package [@R-DHARMa], including tests
    for outliers.

### Model Comparison and Fit Indices

We compared the null, intermediate, and final models using the following
criteria:

-   *Variance partition coefficient (VPC):* The proportion of total
    variance attributable to between-participant differences, computed
    from the variance components of each model. We reported VPCs for
    each model to show how the inclusion of predictors explained
    between-participant variation.
-   *Akaike Information Criterion (AIC)* and *Bayesian Information
    Criterion (BIC):* Lower values indicated better model fit with
    parsimony penalties.
-   *Area Under the Receiver Operating Characteristic Curve (AUC):*
    Computed from in-sample predicted probabilities using the `pROC`
    package [@R-pROC]. The AUC quantified the model's discriminative
    ability, that is, how well predicted probabilities distinguished
    between "success" and "failure" predictions.

Fixed effects were reported as odds ratios (ORs) with Wald-based 95%
confidence intervals and $p$-values. A summary table presented these
estimates alongside VPCs, AIC, BIC, and AUC for all three models,
following the tabular format recommended by the LEVEL guidelines
[@monsalves2020level].

### Interpretation of Possible Outcomes

Different possible outcomes and our respective interpretation are
presented in \@ref(tab:possible-outcomes). Given the current data, OMC
positively and negatively predicting replicability is not the case.

(#tab:possible-outcomes) Possible outcomes and their interpretations.

| OMC and Replicability Hypothesis | OMC and Prediction Hypothesis | Researchers vs. Non-Researchers hypothesis | Interpretation |
|:-----------------|:-----------------|:-----------------|:------------------|
| OMC unrelated to replicability | Participants rely on IF | Researchers rely more | Researchers use a heuristic that lacks validity |
| OMC unrelated to replicability | Participants do not rely on IF | — | OMC is neither valid nor used; no misalignment |
| OMC positively predicts replicability | Participants rely on IF | Researchers rely more | Researchers use a partially valid heuristic |
| OMC negatively predicts replicability | Participants rely on IF | Researchers rely more | Researchers use a counter-valid heuristic |

### Sample Size Considerations

Because participant recruitment occurred through voluntary engagement
with an online game, the sample size was not fully predetermined by
traditional laboratory scheduling. However, we set a minimum recruitment
target of 100 researchers (defined as PhD students, postdocs, or
professors, or participants holding a PhD) and 100 non-researchers, each
completing at least five valid trials. Data collection will remain open
for at least two months after the game's public launch, that is, from
May 20 until July 20.

We reported the final number of participants and trials at each level
after applying all exclusion criteria. We reported the median and range
of trials per participant, as the number of trials varied across
participants depending on their game performance (i.e., how many lives
they retained). The VPCs estimated from the null model were used to
compute post-hoc variance inflation factors
($\text{VIF} = 1 + (\bar{n}_j - 1) \times \text{VPC}$, wher $\bar{n}_j$
was the average number of trials per participant) to contextualize the
effective sample size.
