---
title: "Replicability and Journal Impact Factor"
author: "Jessica Röseler"
format:
  html:
    embed-resources: true
editor: visual
---

```{r}
#| label: setup
#| include: false
#| warning: false
#| message: false

if(!require(readr)) install.packages("readr")
if(!require(dplyr)) install.packages("dplyr")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(scales)) install.packages("scales")
if(!require(quanteda)) install.packages("quanteda", type = "binary")
if(!require(quanteda.textstats)) install.packages("quanteda.textstats")
if(!require(mgcv)) install.packages("mgcv")
if(!require(pROC)) install.packages("pROC")
if(!require(lme4)) install.packages("lme4")
if(!require(DHARMa)) install.packages("DHARMa")
if(!require(detectseparation)) install.packages("detectseparation")
if(!require(rms)) install.packages("rms")

library(readr)
library(dplyr)
library(ggplot2)
library(scales)
library(quanteda)
library(quanteda.textstats)
library(mgcv)
library(pROC)
library(lme4)
library(DHARMa)
library(detectseparation)
library(rms)

set.seed(123)
options(scipen = 999)

#study data base we actually sample from for GutheR
GutheR_studies <- read.csv("Game/dataset.csv")  

#study data base available over FlorA (including studies that are actually excluded e.g. mixed replication outcome)
flora_studies <- read.csv("Game/flora_with_if.csv")
```

```{r}
###############################################################################
# 1. filter irrelevant flora studies 
###############################################################################

flora_studies <- flora_studies[flora_studies$outcome %in% c("successful","failed"),]

flora_studies <- flora_studies[flora_studies$impact_factor<35,]

table(flora_studies$outcome)
table(flora_studies$outcome)/length(flora_studies$outcome)


###############################################################################
# 2. descriptive analysis with 2 outcomes(failed vs successful) -------------
###############################################################################
flora_studies$outcome_fac_bin <- factor(flora_studies$outcome, 
                                      levels = c("failed", "successful"))
plot_data <- flora_studies[flora_studies$outcome %in% c("failed", "successful"),]
ggplot(plot_data, aes(x = impact_factor, fill = outcome_fac_bin)) +
  geom_density(position = "fill", alpha = 0.8) +
  scale_fill_manual(values = c("failed" = "#e41a1c", "successful" = "#4daf4a"),
                    name = "Replikations-Ergebnis") +
  labs(title = "Anteil der Replikationsergebnisse nach Impact Factor",
       x = "Impact Factor",
       y = "Anteil (Proportion)") +
  theme_minimal()

ggplot(plot_data, aes(x = impact_factor, fill = outcome_fac_bin)) +
  geom_histogram(position = "stack", binwidth = 1, alpha = 0.8, color = "white", linewidth = 0.1) +
  scale_fill_manual(values = c("failed" = "#e41a1c", 
                               "successful" = "#4daf4a"),
                    name = "Replikations-Ergebnis") +
  labs(title = "Absolute Verteilung der Ergebnisse nach Impact Factor",
       x = "Impact Factor",
       y = "Anzahl der Studien (Count)") +
  theme_minimal()

###############################################################################
# 3. Model 2 outcomes(failed vs successful) -------------
###############################################################################

flora_studies$outcome_binary <- ifelse(flora_studies$outcome == "failed", 0, ifelse(flora_studies$outcome == "successful", 1, NA))
flora_studies$impact_factor_log <- log(flora_studies$impact_factor+1)

sum(is.na(flora_studies$impact_factor))
sum(flora_studies$impact_factor == 0, na.rm = TRUE) 

# is log impact factor necessary for logreg?
flora_bt2 <- flora_studies[flora_studies$impact_factor > 0, ]
flora_bt2$bt_term_raw <- flora_bt2$impact_factor * log(flora_bt2$impact_factor)

log_reg_bt_raw <- glm(outcome_binary ~ impact_factor + bt_term_raw,
                      family = binomial(link = "logit"),
                      data = flora_bt2)
summary(log_reg_bt_raw) #yes because bt_term is sig

ggplot(flora_studies, aes(x = impact_factor, y = outcome_binary)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              method.args = list(family = binomial), color = "blue") +
  labs(title = "Linearity Check: Impact Factor vs. Binary Outcome",
       x = "Impact Factor", y = "Predicted Probability")

# is logreg generally possible for log impact factor or is the preassumption of linearity between predictor and logodds still not met
flora_bt <- flora_studies[flora_studies$impact_factor_log > 0, ]
flora_bt$bt_term <- flora_bt$impact_factor_log * log(flora_bt$impact_factor_log)

log_reg_bt <- glm(outcome_binary ~ impact_factor_log + bt_term,
                  family = binomial(link = "logit"),
                  data = flora_bt)
summary(log_reg_bt)# pre requirement is given, logreg is possible

ggplot(flora_studies, aes(x = impact_factor_log, y = outcome_binary)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              method.args = list(family = binomial), color = "blue") +
  labs(title = "Linearity Check: Log Impact Factor vs. Binary Outcome",
       x = "Impact Factor", y = "Predicted Probability")


# logistic regression with log impact factor
log_reg_FLorA_log <- glm(outcome_binary~impact_factor_log, family = binomial(link = "logit"), data = flora_studies)
summary(log_reg_FLorA_log)


#omni bus test
modelchi <- log_reg_FLorA_log$null.deviance - log_reg_FLorA_log$deviance
chidf <- log_reg_FLorA_log$df.null - log_reg_FLorA_log$df.residual
chisqp <- 1-pchisq(modelchi, chidf)
chisqp # model is significant overall
# OR and 95% KI
exp(cbind(OR = coef(log_reg_FLorA_log), confint(log_reg_FLorA_log)))

#model visualisation
pred_data <- data.frame(
  impact_factor = seq(min(flora_studies$impact_factor, na.rm = TRUE),
                      max(flora_studies$impact_factor, na.rm = TRUE),
                      length.out = 500)
)
pred_data$impact_factor_log <- log(pred_data$impact_factor + 1)

pred <- predict(log_reg_FLorA_log, newdata = pred_data, 
                type = "link", se.fit = TRUE)
pred_data$prob    <- plogis(pred$fit)
pred_data$lower   <- plogis(pred$fit - 1.96 * pred$se.fit)
pred_data$upper   <- plogis(pred$fit + 1.96 * pred$se.fit)

# P=0.5 Threshold: β0 + β1*log(IF+1) = 0 → IF = exp(-β0/β1) - 1
b0 <- coef(log_reg_FLorA_log)[1]
b1 <- coef(log_reg_FLorA_log)[2]
threshold_IF <- exp(-b0 / b1) - 1
cat("P(success) = 0.5 | Impact Factor:", round(threshold_IF, 2), "\n")

ggplot(pred_data, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob), color = "blue", linewidth = 1) +
  geom_jitter(data = flora_studies,
              aes(x = impact_factor, y = outcome_binary),
              alpha = 0.15, height = 0.03, width = 0) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_vline(xintercept = threshold_IF, linetype = "dashed", color = "red",
             linewidth = 0.8) +
  annotate("text", x = threshold_IF + 0.5, y = 0.45,
           label = paste0("IF = ", round(threshold_IF, 2)),
           color = "red", hjust = 0) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(title = "Logistic Regression: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(successful replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

#GAM model
modell_gam <- gam(outcome_binary ~ s(impact_factor_log), data = flora_studies, family = binomial)
summary(modell_gam)
plot(modell_gam, shade = TRUE, 
     xlab = "impact factor (log)", 
     ylab = "Effect on log-Odds")

# model prediction on original Impact Factor scale
pred_gam <- data.frame(
  impact_factor = seq(min(flora_studies$impact_factor, na.rm = TRUE),
                      max(flora_studies$impact_factor, na.rm = TRUE),
                      length.out = 500)
)
pred_gam$impact_factor_log <- log(pred_gam$impact_factor + 1)

# calculate CI on link scale, then transform on probabilities
pred <- predict(modell_gam, newdata = pred_gam, type = "link", se.fit = TRUE)
pred_gam$prob  <- plogis(pred$fit)
pred_gam$lower <- plogis(pred$fit - 1.96 * pred$se.fit)
pred_gam$upper <- plogis(pred$fit + 1.96 * pred$se.fit)

ggplot(pred_gam, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob), color = "blue", linewidth = 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_jitter(data = flora_studies,
              aes(x = impact_factor, y = outcome_binary),
              alpha = 0.15, height = 0.03, width = 0) +
  scale_y_continuous(limits = c(0, 1), labels = percent_format()) +
  labs(title = "GAM: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(successful replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

## illustrating studies that are only incldued in flora but not in guther:
flora_studies$in_guther <- paste(flora_studies$doi_o, flora_studies$doi_r) %in%
                           paste(GutheR_studies$doi_o, GutheR_studies$doi_r)

ggplot(pred_gam, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob), color = "blue", linewidth = 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_jitter(data = flora_studies,
              aes(x = impact_factor, y = outcome_binary, color = in_guther),
              alpha = 0.5, height = 0.2, width = 0) +
  scale_color_manual(values = c("TRUE" = "gray40", "FALSE" = "orange"),
                     labels = c("TRUE" = "in GutheR", "FALSE" = "only in FLorA"),
                     name = "") +
  scale_y_continuous(limits = c(0, 1), labels = percent_format()) +
  labs(title = "GAM: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(successful replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

# Comparison of Models

##AIC
AIC(log_reg_FLorA_log, modell_gam)

##McFadden R2
null_model <- glm(outcome_binary ~ 1, family = binomial, data = flora_studies)

r2_logreg <- 1 - logLik(log_reg_FLorA_log) / logLik(null_model)
r2_gam    <- 1 - logLik(modell_gam)         / logLik(null_model)

cat("McFadden R² LogReg:", round(r2_logreg, 4), "\n")
cat("McFadden R² GAM:   ", round(r2_gam, 4),    "\n")

##AUC
roc_logreg <- roc(log_reg_FLorA_log$y, fitted(log_reg_FLorA_log))
auc(roc_logreg)

roc_gam <- roc(modell_gam$y, predict(modell_gam, type = "response"))
auc(roc_gam)

###############################################################################
# Does discipline confound relationship of impact factor and replicability?
###############################################################################

DISCIPLINES <- readRDS("disciplines.rds")

normalize <- function(x) {
  x <- tolower(x)
  x <- gsub("[^a-z0-9 ]", " ", x) 
  x <- gsub("\\s+", " ", x)        
  x <- trimws(x)
  return(x)
}

# 3. Lookup-Table: 
lookup <- data.frame(
  journal_norm = normalize(unlist(DISCIPLINES)),
  discipline   = rep(names(DISCIPLINES), lengths(DISCIPLINES)),
  stringsAsFactors = FALSE
)

# 4. Matching
flora_studies$journal_norm <- normalize(flora_studies$journal_o)
flora_studies$discipline   <- lookup$discipline[
  match(flora_studies$journal_norm, lookup$journal_norm)
]

# 5. Diagnostics
cat("Matched:    ", sum(!is.na(flora_studies$discipline)), "\n")
cat("Not found:", sum( is.na(flora_studies$discipline)), "\n")
cat("Proportion NA:     ", round(mean(is.na(flora_studies$discipline)) * 100, 1), "%\n")


# How many cases per discipline
table(flora_studies$discipline, useNA = "always")

# Basic Model (only random intercept)
modell_null <- glmer(outcome_binary ~ 1 + (1 | discipline),
                     family = binomial,
                     data = flora_studies)

# Multilevel-Model with Impact Factor
modell_ml <- glmer(outcome_binary ~ impact_factor_log + (1 | discipline),
                   family = binomial,
                   data = flora_studies)

summary(modell_ml)

# ICC: Proportion of Variance explained by discipline
# binary models: Level-1-Variance = π²/3 ≈ 3.29
tau2 <- as.numeric(VarCorr(modell_ml)$discipline)
icc  <- tau2 / (tau2 + (pi^2 / 3))
cat("ICC:", round(icc, 3), "\n")

# comparison: does impact factor explain variance when discipline is included?
anova(modell_null, modell_ml)

# AIC-comparison with simple LogReg without random effect
AIC(log_reg_FLorA_log, modell_null, modell_ml)#attention with interpretation it's not sound

########################### Check of Prerequirements

#singularity
cat("Singular?:", isSingular(modell_ml, tol = 1e-4), "\n")

#convergence
if (!is.null(modell_ml@optinfo$conv$lme4$messages))
  warning(paste(modell_ml@optinfo$conv$lme4$messages, collapse = " | "))

#separation
detect_sep <- glm(outcome_binary ~ impact_factor_log,
                  data   = flora_studies,
                  family = binomial,
                  method = "detect_separation")
if (detect_sep$outcome == TRUE) {
  warning("Perfect separation detected - coefficients and SE not valid")
  print(detect_sep)
} else {
  cat("No separation detected.\n")
}

# QQ-Plot Random Effects (discipline) - check for normal distribution of random effect
re <- ranef(modell_ml)$discipline
qqnorm(re[["(Intercept)"]], main = "QQ-Plot: Random Intercept (discipline)")
qqline(re[["(Intercept)"]], col = "firebrick")

# Linearity of Predictor
flora_studies$discipline <- as.factor(flora_studies$discipline)

gam_check <- gam(
  outcome_binary ~ s(impact_factor_log) + s(discipline, bs = "re"),
  data   = flora_studies,
  family = binomial,
  method = "REML"
)
summary(gam_check)  # edf ~1 → linear; > 2-3 → non-linear
plot(gam_check, pages = 1, residuals = TRUE, shade = TRUE)

#DHARMa Residuals
sim_res <- simulateResiduals(modell_ml, n = 500)
plot(sim_res)
testDispersion(sim_res)
testOutliers(sim_res)
```

Although impact factor emerged as a statistically significant predictor
of replication success, its practical relevance is negligible. Both
logistic regression and the more flexible GAM yielded AUC values barely
above chance level (0.56 and 0.58, respectively), with McFadden's
pseudo-R² below .02 across all models. Multilevel modeling further
revealed that impact factor and scientific discipline are partially
confounded (ICC = .046), yet impact factor retained a small but
significant independent effect after accounting for disciplinary
clustering. Taken together, while the effect is statistically
detectable, its explanatory power is too limited for impact factor to
serve as a meaningful heuristic for judging the replicability of
individual studies.

```{r}
###############################################################################
# 4. GutheR studies analysis desciptive analysis with 2 outcomes(failed vs successful) -------------

###############################################################################
###############################################################################
# 1. filter irrelevant GutheR studies 
###############################################################################

GutheR_studies <- GutheR_studies[GutheR_studies$outcome %in% c("success","failure"),]

GutheR_studies <- GutheR_studies[GutheR_studies$impact_factor<35,]

table(GutheR_studies$outcome)
table(GutheR_studies$outcome)/length(GutheR_studies$outcome)


###############################################################################
# 2. descriptive analysis with 2 outcomes(failure vs success) -------------
###############################################################################
GutheR_studies$outcome_fac_bin <- factor(GutheR_studies$outcome, 
                                      levels = c("failure", "success"))
plot_data <- GutheR_studies[GutheR_studies$outcome %in% c("failure", "success"),]
ggplot(plot_data, aes(x = impact_factor, fill = outcome_fac_bin)) +
  geom_density(position = "fill", alpha = 0.8) +
  scale_fill_manual(values = c("failure" = "#e41a1c", "success" = "#4daf4a"),
                    name = "Replication Result") +
  labs(title = "Proportion of Replicationresult per Impact Factor",
       x = "Impact Factor",
       y = "Proportion") +
  theme_minimal()

ggplot(plot_data, aes(x = impact_factor, fill = outcome_fac_bin)) +
  geom_histogram(position = "stack", binwidth = 1, alpha = 0.8, color = "white", linewidth = 0.1) +
  scale_fill_manual(values = c("failure" = "#e41a1c", 
                               "success" = "#4daf4a"),
                    name = "Replication Result") +
  labs(title = "Absolute Distribution of Replicationresult per Impact Factor",
       x = "Impact Factor",
       y = "Study Count") +
  theme_minimal()

###############################################################################
# 3. Model 2 outcomes(failed vs successful) -------------
###############################################################################

GutheR_studies$outcome_binary <- ifelse(GutheR_studies$outcome == "failure", 0, ifelse(GutheR_studies$outcome == "success", 1, NA))
GutheR_studies$impact_factor_log <- log(GutheR_studies$impact_factor+1)

sum(is.na(GutheR_studies$impact_factor))
sum(GutheR_studies$impact_factor == 0, na.rm = TRUE) 

# is log impact factor necessary for logreg?
GutheR_bt2 <- GutheR_studies[GutheR_studies$impact_factor > 0, ]
GutheR_bt2$bt_term_raw <- GutheR_bt2$impact_factor * log(GutheR_bt2$impact_factor)

log_reg_bt_raw <- glm(outcome_binary ~ impact_factor + bt_term_raw,
                      family = binomial(link = "logit"),
                      data = GutheR_bt2)
summary(log_reg_bt_raw) #yes because bt_term is sig

ggplot(GutheR_studies, aes(x = impact_factor, y = outcome_binary)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              method.args = list(family = binomial), color = "blue") +
  labs(title = "Linearity Check: Impact Factor vs. Binary Outcome",
       x = "Impact Factor", y = "Predicted Probability")

# is logreg generally possible for log impact factor or is the preassumption of linearity between predictor and logodds still not met
GutheR_bt <- GutheR_studies[GutheR_studies$impact_factor_log > 0, ]
GutheR_bt$bt_term <- GutheR_bt$impact_factor_log * log(GutheR_bt$impact_factor_log)

log_reg_bt <- glm(outcome_binary ~ impact_factor_log + bt_term,
                  family = binomial(link = "logit"),
                  data = GutheR_bt)
summary(log_reg_bt)# pre requirement is not given, look at GAM and watch out for differences

ggplot(GutheR_studies, aes(x = impact_factor_log, y = outcome_binary)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              method.args = list(family = binomial), color = "blue") +
  labs(title = "Linearity Check: Log Impact Factor vs. Binary Outcome",
       x = "Impact Factor", y = "Predicted Probability")


# logistic regression with log impact factor
log_reg_GutheR_log <- glm(outcome_binary~impact_factor_log, family = binomial(link = "logit"), data = GutheR_studies)
summary(log_reg_GutheR_log)


#omni bus test
modelchi <- log_reg_GutheR_log$null.deviance - log_reg_GutheR_log$deviance
chidf <- log_reg_GutheR_log$df.null - log_reg_GutheR_log$df.residual
chisqp <- 1-pchisq(modelchi, chidf)
chisqp # model is significant overall
# OR and 95% KI
exp(cbind(OR = coef(log_reg_GutheR_log), confint(log_reg_GutheR_log)))

#model visualisation
pred_data <- data.frame(
  impact_factor = seq(min(GutheR_studies$impact_factor, na.rm = TRUE),
                      max(GutheR_studies$impact_factor, na.rm = TRUE),
                      length.out = 500)
)
pred_data$impact_factor_log <- log(pred_data$impact_factor + 1)

pred <- predict(log_reg_GutheR_log, newdata = pred_data, 
                type = "link", se.fit = TRUE)
pred_data$prob    <- plogis(pred$fit)
pred_data$lower   <- plogis(pred$fit - 1.96 * pred$se.fit)
pred_data$upper   <- plogis(pred$fit + 1.96 * pred$se.fit)

# P=0.5 Threshold: β0 + β1*log(IF+1) = 0 → IF = exp(-β0/β1) - 1
b0 <- coef(log_reg_GutheR_log)[1]
b1 <- coef(log_reg_GutheR_log)[2]
threshold_IF <- exp(-b0 / b1) - 1
cat("P(success) = 0.5 | Impact Factor:", round(threshold_IF, 2), "\n")

ggplot(pred_data, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob), color = "blue", linewidth = 1) +
  geom_jitter(data = GutheR_studies,
              aes(x = impact_factor, y = outcome_binary),
              alpha = 0.15, height = 0.03, width = 0) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_vline(xintercept = threshold_IF, linetype = "dashed", color = "red",
             linewidth = 0.8) +
  annotate("text", x = threshold_IF + 0.5, y = 0.45,
           label = paste0("IF = ", round(threshold_IF, 2)),
           color = "red", hjust = 0) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(title = "Logistic Regression: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(success replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

#ALTERNATIVE: Restricted Cubic Splines Logistic Regression Cause box tidwell test was significant even with log impact factor:

guther_rcs_data <- GutheR_studies[!is.na(GutheR_studies$outcome_binary) & 
                                   !is.na(GutheR_studies$impact_factor_log), ]

dd <- datadist(guther_rcs_data)
options(datadist = "dd")

log_reg_rcs <- lrm(outcome_binary ~ rcs(impact_factor_log, 4), 
                   data = guther_rcs_data)

# Visualisierung
ggplot(Predict(log_reg_rcs, impact_factor_log, fun = plogis))

pred_data$impact_factor_log <- log(pred_data$impact_factor + 1)

pred_rcs <- predict(log_reg_rcs, 
                    newdata = pred_data, 
                    type = "lp",  # link scale
                    se.fit = TRUE)

pred_data$prob_rcs  <- plogis(pred_rcs$linear.predictors)
pred_data$lower_rcs <- plogis(pred_rcs$linear.predictors - 1.96 * pred_rcs$se.fit)
pred_data$upper_rcs <- plogis(pred_rcs$linear.predictors + 1.96 * pred_rcs$se.fit)

# P=0.5 Threshold: numerical identification
crossings <- which(diff(sign(pred_data$prob_rcs - 0.5)) != 0)
threshold_IF <- pred_data$impact_factor[crossings[1]]
cat("P(success) = 0.5 | Impact Factor:", round(threshold_IF, 2), "\n")

ggplot(pred_data, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower_rcs, ymax = upper_rcs), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob_rcs), color = "blue", linewidth = 1) +
  geom_jitter(data = GutheR_studies,
              aes(x = impact_factor, y = outcome_binary),
              alpha = 0.15, height = 0.03, width = 0) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_vline(xintercept = threshold_IF, linetype = "dashed", color = "red",
             linewidth = 0.8) +
  annotate("text", x = threshold_IF + 0.5, y = 0.45,
           label = paste0("IF = ", round(threshold_IF, 2)),
           color = "red", hjust = 0) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(title = "Restricted Cubic Splines Logistic Regression: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(success replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

#GAM model
modell_gam <- gam(outcome_binary ~ s(impact_factor_log), data = GutheR_studies, family = binomial)
summary(modell_gam)
plot(modell_gam, shade = TRUE, 
     xlab = "impact factor (log)", 
     ylab = "Effect on log-Odds")

# model prediction on original Impact Factor scale
pred_gam <- data.frame(
  impact_factor = seq(min(GutheR_studies$impact_factor, na.rm = TRUE),
                      max(GutheR_studies$impact_factor, na.rm = TRUE),
                      length.out = 500)
)
pred_gam$impact_factor_log <- log(pred_gam$impact_factor + 1)

# calculate CI on link scale, then transform on probabilities
pred <- predict(modell_gam, newdata = pred_gam, type = "link", se.fit = TRUE)
pred_gam$prob  <- plogis(pred$fit)
pred_gam$lower <- plogis(pred$fit - 1.96 * pred$se.fit)
pred_gam$upper <- plogis(pred$fit + 1.96 * pred$se.fit)

ggplot(pred_gam, aes(x = impact_factor)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "blue", alpha = 0.15) +
  geom_line(aes(y = prob), color = "blue", linewidth = 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40") +
  geom_jitter(data = GutheR_studies,
              aes(x = impact_factor, y = outcome_binary),
              alpha = 0.15, height = 0.03, width = 0) +
  scale_y_continuous(limits = c(0, 1), labels = percent_format()) +
  labs(title = "GAM: Impact Factor vs. probability of replication",
       x = "Impact Factor",
       y = "P(success replication)",
       caption = "grey: 95%-CI; dashed: P = 0.5 threshold") +
  theme_minimal()

# Comparison of Models

##AIC
AIC(log_reg_GutheR_log, modell_gam, log_reg_rcs)

##McFadden R2
null_model <- glm(outcome_binary ~ 1, family = binomial, data = GutheR_studies)

r2_logreg <- 1 - logLik(log_reg_GutheR_log) / logLik(null_model)
r2_gam    <- 1 - logLik(modell_gam)         / logLik(null_model)
r2_rcs    <- 1 - logLik(log_reg_rcs)         / logLik(null_model)

cat("McFadden R² LogReg:", round(r2_logreg, 4), "\n")
cat("McFadden R² GAM:   ", round(r2_gam, 4),    "\n")
cat("McFadden R² RCS:   ", round(r2_rcs,    4), "\n")

##AUC
roc_logreg <- roc(log_reg_GutheR_log$y, fitted(log_reg_GutheR_log))
auc(roc_logreg)

roc_gam <- roc(modell_gam$y, predict(modell_gam, type = "response"))
auc(roc_gam)

roc_rcs <- roc(guther_rcs_data$outcome_binary,
               plogis(log_reg_rcs$linear.predictors))
auc(roc_rcs)
###############################################################################
# Does discipline confound relationship of impact factor and replicability?
###############################################################################

DISCIPLINES <- readRDS("disciplines.rds")

normalize <- function(x) {
  x <- tolower(x)
  x <- gsub("[^a-z0-9 ]", " ", x) 
  x <- gsub("\\s+", " ", x)        
  x <- trimws(x)
  return(x)
}

# 3. Lookup-Table: 
lookup <- data.frame(
  journal_norm = normalize(unlist(DISCIPLINES)),
  discipline   = rep(names(DISCIPLINES), lengths(DISCIPLINES)),
  stringsAsFactors = FALSE
)

# 4. Matching
GutheR_studies$journal_norm <- normalize(GutheR_studies$journal)
GutheR_studies$discipline   <- lookup$discipline[
  match(GutheR_studies$journal_norm, lookup$journal_norm)
]

# 5. Diagnostics
cat("Matched:    ", sum(!is.na(GutheR_studies$discipline)), "\n")
cat("Not found:", sum( is.na(GutheR_studies$discipline)), "\n")
cat("Proportion NA:     ", round(mean(is.na(GutheR_studies$discipline)) * 100, 1), "%\n")


# How many cases per discipline
table(GutheR_studies$discipline, useNA = "always")

# Basic Model (only random intercept)
modell_null <- glmer(outcome_binary ~ 1 + (1 | discipline),
                     family = binomial,
                     data = GutheR_studies)

# Multilevel-Model with Impact Factor
modell_ml <- glmer(outcome_binary ~ impact_factor_log + (1 | discipline),
                   family = binomial,
                   data = GutheR_studies)

summary(modell_ml)

# ICC: Proportion of Variance explained by discipline
# binary models: Level-1-Variance = π²/3 ≈ 3.29
tau2 <- as.numeric(VarCorr(modell_ml)$discipline)
icc  <- tau2 / (tau2 + (pi^2 / 3))
cat("ICC:", round(icc, 3), "\n")

# comparison: does impact factor explain variance when discipline is included?
anova(modell_null, modell_ml)

# AIC-comparison with simple LogReg without random effect
AIC(log_reg_GutheR_log, modell_null, modell_ml)#attention with interpretation it's not sound

########################### Check of Prerequirements

#singularity
cat("Singular?:", isSingular(modell_ml, tol = 1e-4), "\n")

#convergence
if (!is.null(modell_ml@optinfo$conv$lme4$messages))
  warning(paste(modell_ml@optinfo$conv$lme4$messages, collapse = " | "))

#separation
detect_sep <- glm(outcome_binary ~ impact_factor_log,
                  data   = GutheR_studies,
                  family = binomial,
                  method = "detect_separation")
if (detect_sep$outcome == TRUE) {
  warning("Perfect separation detected - coefficients and SE not valid")
  print(detect_sep)
} else {
  cat("No separation detected.\n")
}

# QQ-Plot Random Effects (discipline) - check for normal distribution of random effect
re <- ranef(modell_ml)$discipline
qqnorm(re[["(Intercept)"]], main = "QQ-Plot: Random Intercept (discipline)")
qqline(re[["(Intercept)"]], col = "firebrick")

# Linearity of Predictor
GutheR_studies$discipline <- as.factor(GutheR_studies$discipline)

gam_check <- gam(
  outcome_binary ~ s(impact_factor_log) + s(discipline, bs = "re"),
  data   = GutheR_studies,
  family = binomial,
  method = "REML"
)
summary(gam_check)  # edf ~1 → linear; > 2-3 → non-linear
plot(gam_check, pages = 1, residuals = TRUE, shade = TRUE)

#DHARMa Residuals
sim_res <- simulateResiduals(modell_ml, n = 500)
plot(sim_res)
testDispersion(sim_res)
testOutliers(sim_res)


```

Although impact factor emerged as a statistically significant predictor
of replication success over different models like logistic regression,
GAM and restricted cubic splines logistic regression, its practical
relevance is negligible. The Box-Tidwell test indicated a violation of
the linearity assumption for logistic regression even after
log-transformation, favoring more flexible approaches. Nonetheless, GAM
and Restricted Cubic Splines yielded no meaningful improvement over
simple logistic regression, with AUC values across all three models
hovering around 0.56 and McFadden's pseudo-R² ranging from .008 to .013.
The RCS model identified a threshold of P(success) = 0.5 at an impact
factor of approximately 3.1, though the wide confidence intervals and
negligible model fit limit the interpretability of this estimate.
Multilevel modeling revealed that scientific discipline accounts for a
small but non-trivial share of variance in replication success (ICC =
.052), and impact factor and discipline are partially confounded.
Nevertheless, impact factor retained a small independent effect after
accounting for disciplinary clustering (β = −0.40, p \< .001). Model
diagnostics indicated no issues with overdispersion, outliers, or
separation. Taken together, while the effect of impact factor is
statistically detectable and robust across model specifications, its
explanatory power is too limited to serve as a meaningful heuristic for
judging the replicability of individual studies.

```{r}

#####################################################################
# Where are differences between the two datasets
#####################################################################

# Distribution of impact_factor_log
summary(GutheR_studies$impact_factor_log)
summary(flora_studies$impact_factor_log)

# Visual comparison
par(mfrow = c(1, 2))
hist(GutheR_studies$impact_factor_log, main = "GutheR (n=1171)")
hist(flora_studies$impact_factor_log, main = "flora (n=1515)")
par(mfrow = c(1, 1))

# Density comparison
plot(density(GutheR_studies$impact_factor_log, na.rm = TRUE), col = "blue", main = "Comparison impact_factor_log")
lines(density(flora_studies$impact_factor_log, na.rm = TRUE), col = "red")
legend("topright", c("GutheR", "flora"), col = c("blue", "red"), lty = 1)

# outcome_binary distribution
prop.table(table(GutheR_studies$outcome_binary))
prop.table(table(flora_studies$outcome_binary))

```
